---
title: "Intro to the PheGWAS package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{PheGWAS-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{dplyr}
  %\VignetteDepends{httr}
  %\VignetteDepends{jsonlite}
  %\VignetteDepends{xml2}
  %\VignetteDepends{stringr}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",fig.width=12, fig.height=9, message=FALSE, tidy=TRUE, dpi=75)
```

```{r setup}
library(PheGWAS)
```

Following processed summary data are from the lipid consortium:

```{r}
head(hdl)
```
```{r}
head(ldl)
```
```{r}
head(trig)
```
```{r}
head(tchol)
```

Following processed summary data are from the giant consortium:

```{r}
head(bmimen)
```
```{r}
head(bmiwomen)
```

The dataframe’s are passed to processphegwas function as a list of dataframe’s.

```{r}
x <- list(hdl,ldl,trig,tchol)
phenos <- c("HDL","LDL","TRIGS","TOTALCHOLESTROL")
```

This preprocess the dataframes’ for passing to the landscape function.
```{r}
y <- processphegwas(x,phenos)
```

3D landscape visualization of all the phenotypes across the base pair #positions
```{r}
landscape(y)
```

3D landscape visualization of all the phenotypes across the base pair #positions, showing only the crusts above a certain threshold
```{r}
landscape(y,sliceval = 10)
```

3D landscape visualization of all the phenotypes across the base pair #positions, showing only the crusts that are within a certain region (between sliceval and upperlimit)
```{r}
landscape(y,sliceval = 10 ,chromosome = 19,upperlimit = 50)
```

3D landscape visualization of chromosome number 16, with bp division on #1,000,000 (default is 1,000,000)
```{r}
landscape(y,sliceval = 7.5,chromosome = 19)
```

3D landscape visualization of chromosome number 16, with bp division on #1,000,000. Gene View is active
```{r}
landscape(y,sliceval = 7.5,chromosome = 19, geneview = TRUE)
```

Effect size plot
```{r}
landscape(y,sliceval = 7.5,chromosome = 16,bpdivision = 1000000, betaplot = TRUE)
```

3D visualization with LD block (for european population) passing externally, parameter to pass LD and also calculate the mutualLD block 

```{r}
landscape(y, sliceval = 30, chromosome = 19,bpdivision= 1000000,calculateLD= TRUE,mutualLD = TRUE)
```
